%	Section Title
\cvsection{Experience}

%	Content
\begin{cventries}

  \cventry
    {Software engineer (Go • Technical Team Leader)}
    {\href{https://www.KBTG.tech}{Kasikorn Business-Technology Group (KBTG)}}
    {Thailand}
    {2020 - Current}
     {
      \begin{cvitems}
        \item {Requirement gathering and analysis. Estimate development effort and time from scope and assign the task to the development team.}
        \item {Make the logical flow/diagram of the program and present to the enterprise architect team to review and approve the solution for development.}
        \item {Design microservices / application arcitecture.}
        \item {Make the API interface documents, production deployment documents.}
        \item {Review the database design \& code review.}
        \item {Meeting with other teams in the banking system for finding the solution and do the impact analysis when making the new feature.}
        \item {Coordinate with the infrastructure team/system engineer team for preparing the environment to deploy the program.}
        \item {Suggest solution and help the team solve the production incident issues by finding the workaround and long-term solution.}
        \item {Knowledge sharing to the new member of the team about the application / system architecture, banking system architecture, tech stack using by the team / in the banking system.}
      \end{cvitems}
    }

  \cventry
    {Associate software engineer (Go • Backend Developer)}
    {\href{https://www.KBTG.tech}{Kasikorn Business-Technology Group (KBTG)}}
    {Thailand}
    {2017-2020}
     {
      \begin{cvitems}
        \item {Building K+shop/Blue Connection Wallet application in the backend side.}
        \item {Use Go to create microservices and connect to the MongoDB / Redis in our own system.}
        \item {Make the API with Go to connect to the legacy application in the banking system with RESTful/SOAP.}
        \item {Investigate production issues and find the workaround / long-term solution.}
      \end{cvitems}
    }

\end{cventries}
